Viscous Transport in Eroding Porous Media

### 2019-07-27 docs/transport/erosion_transport.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A Single Body Close to a Wall}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a single eroding body close to a solid wall.  To compare our
results with a similar numerical experiment performed by Mitchell and
Spagnolie~\cite{mit-spa2017}, rather a pressure drop boundary condition,
we impose the shear flow
\begin{align}
  \UU(\xx)=\left[
  \begin{array}{c}
    y+1 \\ 0
  \end{array}
  \right],
\end{align}
on the outer wall.  The eroding body is initially a circle of
radius $r=0.4$, length $L = 2\pi r$, and is placed near the no-slip wall
at $y=-1$.  We discretize the eroding body with $N_\iin=256$
discretization points, and the center of the eroding body is initially
placed at $h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N\iin$.  For all
three simulations, we use the time step size $\Delta t=10^{-4}$.

With this setup, many of the discretization points on the eroding body
are too close to the outer wall for the trapezoid rule to achieve
sufficient accuracy.  However, by using the Barycentric quadrature rule,
the numerical stable simulations are possible.  In
Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
several equispaced time steps, and the color of indicates the erosion
rate (magnitude of the shear stress).  Comparing our results to Mitchell
and Spagnolie~\cite{mit-spa2017} (Figure 7(b)), we see similar results
where the shear stress is smallest near the zero background flow line
$y=-1$.  Moreover, since the shear stress is everywhere positive, the
erosion rate, which is the magnitude of the shear stress, is a smooth
function.  The result is that the eroding shape does not have any
stagnation points where corners will develop.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A Single Body Close to a Wall}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a single eroding body close to a solid wall.  To compare our
results with a similar numerical experiment performed by Mitchell and
Spagnolie~\cite{mit-spa2017}, rather a pressure drop boundary condition,
we impose the shear flow
\begin{align}
  \UU(\xx)=\left[
  \begin{array}{c}
    y+1 \\ 0
  \end{array}
  \right],
\end{align}
on the outer wall.  In their experiment, Mitchell and Spagnolie place
the center of the eroding body $1.5$ times the body's radius above the
solid wall.  By using the numerical integration scheme described in
Section~\ref{s:method}, the eroding body can be placed much closer to
the solid wall.  In the following experiments, we consider an eroding
body that is initially a circle of radius $r=0.4$ and is placed near the
no-slip wall at $y=-1$.  We discretize the eroding body with
$N_\iin=256$ discretization points, and the center of the eroding body
is initially placed at $h/2$, $h/4$, and $h/10$, where $h = 2\pi
r/N\iin$.  For all three simulations, we use the time step size $\Delta
t=10^{-4}$.

With this setup, many of the discretization points on the eroding body
are too close to the outer wall for the trapezoid rule to achieve
sufficient accuracy.  However, by using the Barycentric quadrature rule,
the numerical stable simulations are possible.  In
Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
several equispaced time steps, and the color of indicates the erosion
rate (magnitude of the shear stress).  Comparing our results to Mitchell
and Spagnolie~\cite{mit-spa2017} (Figure 7(c)), we see similar results.
In particular, between the eroding body and the solid wall the flow is
very small and there is no recirculation, and this is consistent with
three-dimensional results~\cite{cah-feu2002}.  Moreover, for all three
distances, the shear stress is positive \todo[inline]{S-H: Is this
right?  Is the shear stress ever negative?  I might expect so since
there are two stagnation points}, so the erosion is smooth.

where the shear stress is smallest near the zero background flow line
$y=-1$.  Moreover, since the shear stress is everywhere positive, the
erosion rate, which is the magnitude of the shear stress, is a smooth
function.  The result is that the eroding shape does not have any
stagnation points where corners will develop.
